Paper Analysis

### 2025-05-07 Paper_WriteUp/Paper_Plots.qmd
updating filenames for fig2

ggsave(plot = fig2a, 
       filename = paste0(here("Paper_WriteUp", "paper_figures",
                              "time_between_games_gm.png")), dpi = 600,
       height = 4, width = 6.25)

@@

ggsave(plot = fig2b, 
       filename = paste0(here("Paper_WriteUp", "paper_figures",
                              "session_length_gm.png")), dpi = 600,
       height = 4, width = 6.25)
```

>>>>

ggsave(plot = fig2a, 
       filename = paste0(here("Paper_WriteUp", "paper_figures",
                              "fig2a.png")), dpi = 600,
       height = 4, width = 6.25)

@@

ggsave(plot = fig2b, 
       filename = paste0(here("Paper_WriteUp", "paper_figures",
                              "fig2b.png")), dpi = 600,
       height = 4, width = 6.25)
```
